I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-19 Paper/proofs.tex
update proof

	In general, $S$ may not be defined on every node (e.g. if there is a negative and a positive path from $a$ to $c$). However, if there is no compensating pair, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
		For instance, for an input node $a_i$ of any 3 layer DNN:
		\begin{enumerate}
			\item  $S(a_i)=0$ if 
			for all $b_j, W_{a_i b_j}\cdot W_{b_j c} = 0$

			\item  $S(a_i)=1$ if for all $b_j, W_{a_i b_j}\cdot W_{b_j c} \geq 0$ and there exists 
			$j, W_{a_i b_j}\cdot W_{b_j c} > 0$

			\item $S(a_i)=-1$ if for all $b_j\ W_{a_i b_j}\cdot W_{b_j c} \leq 0$ and there exists 
			$j, W_{a_i b_j}\cdot W_{b_j c} < 0$ 
		\end{enumerate}

	For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $W_{b_j c}$ is positive, negative, or 0 respectively. Finally, for the output node $z$, we define $S(z)=1$.

	\begin{lemma}[Sign]
		\label{lemma1}
		Let $L,L'$  consecutive layers of a DNN without compensation, 
		and $m\in L$ $n\in L'$. Then if both 
		$w(m n) \neq 0$ and $S(n) \neq 0$, then 
		$S(m)=S(n)\mathrm{Sign}(W_{n m})$.
	\end{lemma}

@@

		Hence there is a non zero path from $m$ to $z$: $(m n) \pi$, which is of sign 
		$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
		\hfill $\square$
	\end{proof}

@@

	\begin{proof}
		We prove this lemma by induction on layers. For input layer, this is true by definition. Suppose this lemma is true up to layer $L_i$, we need to show this for layer $L_{i+1}$. Let $c$ be a node in layer $L_{i+1}$, then by definition, we have the following equation: \begin{align*}
			c = \boldsymbol{bias}_c+\sum_{b\in L}W_{bc}\ReLU(b).
		\end{align*}

		Therefore we have the following inequalities:\begin{align*}
				\max(c)\leq\sum_{b \in L_i, W_{bc }>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
			\min(c)\geq\sum_{b \in L_i, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bisa}_c
		\end{align*}

		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $W_{bc}>0$; if $S(b)=-1$, then $W_{bc}<0$; if $S(b)=0$, then $W_{bc}=0$.

@@

		So combining formulas and above two facts, we will have that when the input vector is $\vx^*$, \begin{align*}
			\max(c)&\geq\Val_{\vx^*}(c) \\
			&= \sum_{b \in L_i, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L_i, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bisa}_c\\
			&\geq\max(c)
		\end{align*}  Hence $\max(c)=\Val_{\vx^*}(c)$.

@@

%	\begin{lemma}
%		\label{lemma2}
%		Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
%		Then:
%		$$ S(n) \max(S(n) n)=\sum_{m \in L}W_{m n} S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
%		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}W_{m n} S(n)\max(S(n)\hat{m}_s)+bias_n)$$
%		
%		Similarly for minimal value.
%		
%		%	for minimal value,	
%		%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
%			%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}W_{m n)\min(\hat{m}s}+bias_n)$
%		\end{lemma}
%		
%		\begin{proof}
%			We choose $\boldsymbol{x}^*$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
%			that is setting the value for node $a$ be $\max(a)$ for $S(a)=1$ and $\min(a)$ for $S(a)=-1$.
%			At configuration $\boldsymbol{x}^*$, every $a_s(\boldsymbol{x}^*))=\max_{\boldsymbol{x}} {a_s(\boldsymbol{x}))}=\max(a_s)$ is maximized.  
%			
%			Consider any $b$ in the first hidden layer $L_1$.
%			Assume first that $S(b)=+1$.
%			We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} W_{ab} \Val(a) + bias_b$.
%			If every $W_{ab} \Val(a)$ is maximized in the same time, 
%			then $\Val(b_s)= \Val(b)$ is also maximized. 
%			
%			We claim that this is the case at 
%			configuration $\boldsymbol{x}^*$.
%			Indeed, if $W_{ab}=0$, any $\Val(a)$ can be chosen to maximize 
%			$W_{ab}\Val(a)$. If $W_{ab}>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
%			$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $W_{ab}\Val(a)$.
%			Finally, if $W_{a b}<0$ then $S(a_s) = -1$, and we have 
%			$\max(a_s) = min(a)$, maximizing $W_{ab}\Val(a)$.
%			
%			Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
%			$$\max(b)=\sum_{m \in L}W_{a b} \max(a_s)+bias_b$$
%			
%			The case $S(b)=-1$ is symmetric:
%			$\max(b_s)= -\min(b)$ is reached when minimizing $b$, which is also 
%			satisfied at $\boldsymbol{x}^*$.
%			In both case, $\Val(b_s)$ is maximized at $\boldsymbol{x}^*$. Notice that $\boldsymbol{x}^*$ does not depend upon $b$, so choosing $\boldsymbol{x}^*$ uniformly maximize all $\Val(b_s)$.
%			
%			This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
%			$\ReLU(\sum_{m \in L}W_{a }\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
%			
%			We proceed by induction over every layer of the DNN till the output layer, proving that 
%			$\max(z_s)=\max(z)$ is reached at configuration $\boldsymbol{x}^*$.
%			
%			The case for $\min$ is similar, with another input vector $\boldsymbol{x}^\sharp$ instead of $\boldsymbol{x}^*$.
%			\hfill $\square$
%		\end{proof}

@@

		\begin{corollary}
			\label{cor1}
			$$\max(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bias}_c$$
			$$\min(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bias}_c$$
		\end{corollary}

@@

			The Box absraction computes its upper bound using:
			$$\bar{f}(n)= \sum_{W_{mn}>0} W_{mn} \bar{f}(\hat{m}) + \sum_{W_{mn}<0} W_{mn} \underline{f}(\hat{m}) + bias_n$$

@@

				%	 \item $W_{b,z}=0$, or
				%	 \item For every input node $j\in J$, we have $W_{a_j,b}=0$.

@@

			%	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.

@@

			%	Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
			%	Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.

@@

			%	$$b= B^0 +\sum_{a_i\in I} W_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.

@@

			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}W_{b_ha_i}+B_h$ ($B_h$ is the bias). 

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).

@@

			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $W_{b,z}>0$, and the lower bound
			%of its (LP) approximation if $W_{b,z}<0$. 

@@

			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(W_{zb})=1$, then 

@@

			%and if $S(b)=\mathrm{sign}(W_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} W_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
			%	\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).

@@

			%$W_{b,z} = 0$ and $b \in B^2$ iff $W_{b,z} \neq 0$.

@@

			%$$\sum_{b\in B_{pure}} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$

@@

			%For $b \in B^2$, we have $W_{a_j,b}=0$ for all $j \in J$

@@

			%$$\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} W_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
			%=\sum_{b\in B^2} W_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))

@@

				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}W_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))

@@

				\begin{lemma} \label{lem:open_node_2}
					A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
					\begin{enumerate}
					  	\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
					\end{enumerate}

@@

				\begin{proof}
					First, we show that if one of case 1, 2 happens, then $b$ will not be on a weak compensating pair. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $W_{a_j,b}=0$ implies weight$(\pi)=0$.

					Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
					Because 2) does not hold, there is a $j \in J$ with $W_{a_j,b} \neq 0$, say $>0$.
					Because 1) does not hold, $W_{b,z} \neq 0$, say $>0$.
					Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
					from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
					Then $((a_j,b,z), \pi')$ is also a weak compensating pair. \qed
				\end{proof}

				\begin{lemma}\label{lem:subnetwork}
					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$. We call this sub-network $D_I$. In $D_I$, there is no compensating pair.
				\end{lemma}

@@

					1. if $b\in J$, by definition, $W_{bc}=0$.

					2. if $b\in B_{open}$, then $W_{bc}=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.

					3. if $b\in B_{zero}$, then $W_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction. \qed
				\end{proof}

@@

				\begin{lemma}
					If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $W_{bc}S(c)=S(b)$.
				\end{lemma}

@@

				\begin{proof}
					This is because if there exists nodes $b,c$ such that $W_{bc}\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ not in $J$ but this means so does $c$, a contradiction. Therefore any $b$ such that $W_{bc}\neq 0$ is also in above set. \qed
				\end{proof}

@@

				%\begin{lemma}\label{lem:pure_node}
				%	For a node $c\in B_{pure}$, $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$ (and $\LB$ the same) only depends on $\boldsymbol{x}^0_I$.
				%\end{lemma}
				%
				%\begin{proof}
				%	We prove this lemma by induction. For the first hidden layer, this is trivial.
				%	
				%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 +\sum_{b\in B_{zero}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
				%	
				%	
				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $W_{b,c}=0$. And similarly, for any $b\in B_{zero}$, $W_{bc}=0$. Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
					%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
				%\end{proof}

@@

					If $S(c)$ is defined, then consider all $b$ such that $W_{bc}\neq 0$. First, $b$ cannot in $B_{zero}$; so by induction hypothesis, the value of $b$ is fixed under $\boldsymbol{x}^*_I,\boldsymbol{x}^0_J$ in MILP model.

>>>>

	In general, $S$ may not be defined on every node (e.g. if there is a negative and a positive path from $a$ to $c$). However, if there is no compensating pair, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
		For instance, for an input node $a_i$ of any 3 layer DNN:
		\begin{enumerate}
			\item  $S(a_i)=0$ if 
			for all $b_j, weigth(a_i b_j)\cdot weigth(b_j c) = 0$

			\item  $S(a_i)=1$ if for all $b_j, weigth(a_i b_j)\cdot weigth(b_j c) \geq 0$ and there exists 
			$j, weigth(a_i b_j)\cdot weigth(b_j c) > 0$

			\item $S(a_i)=-1$ if for all $b_j\ weigth(a_i b_j)\cdot weigth(b_j c) \leq 0$ and there exists 
			$j, weigth(a_i b_j)\cdot weigth(b_j c) < 0$ 
		\end{enumerate}

	For $b_j$ in the hidden layer, we have $S(b_j)=1,-1,0$ if $weigth(b_j c)$ is positive, negative, or 0 respectively. Finally, for the output node $z$, we define $S(z)=1$.

	\begin{lemma}[Sign]
		\label{lemma1}
		Let $L,L'$  consecutive layers of a DNN without compensation, 
		and $m\in L$ $n\in L'$. Then if both 
		$weigth(mn) \neq 0$ and $S(n) \neq 0$, then 
		$S(m)=S(n)\mathrm{Sign}(weigth(n m))$.
	\end{lemma}

@@

		Hence there is a non zero path from $m$ to $z$: $(m n) \pi$, which is of sign 
		$S(n)\mathrm{Sign}(weigth(n m))$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(weigth(n m))$.
		\hfill $\square$
	\end{proof}

@@

	\begin{proof}
		We prove this lemma by induction on layers. For input layer, this is true by definition. Suppose this lemma is true up to layer $L_i$, we need to show this for layer $L_{i+1}$. Let $c$ be a node in layer $L_{i+1}$, then by definition, we have the following equation: \begin{align*}
			c = \boldsymbol{bias}_c+\sum_{b\in L}weigth(bc)\ReLU(b).
		\end{align*}

		Therefore we have the following inequalities:\begin{align*}
				\max(c)\leq\sum_{b \in L_i, weigth(bc )>0}weigth(bc) \max(\hat{b}) + \sum_{b \in L_i, weigth(bc)<0}weigth(bc) \min(\hat{b}) + \boldsymbol{bisa}_c\\
			\min(c)\geq\sum_{b \in L_i, weigth(bc)>0}weigth(bc) \min(\hat{b}) + \sum_{b \in L_i, weigth(bc)<0}weigth(bc) \max(\hat{b}) + \boldsymbol{bisa}_c
		\end{align*}

		Now, if $S(c)=1$, we consider different case of $b$. If $S(b)=1$, then by Lemma \ref{lem:sign}, $weigth(bc)>0$; if $S(b)=-1$, then $weigth(bc)<0$; if $S(b)=0$, then $weigth(bc)=0$.

@@

		So combining formulas and above two facts, we will have that when the input vector is $\vx^*$, \begin{align*}
			\max(c)&\geq\Val_{\vx^*}(c) \\
			&= \sum_{b \in L_i, weigth(bc)>0}weigth(bc) \max(\hat{b}) + \sum_{b \in L_i, weigth(bc)<0}weigth(bc) \min(\hat{b}) + \boldsymbol{bisa}_c\\
			&\geq\max(c)
		\end{align*}  Hence $\max(c)=\Val_{\vx^*}(c)$.

@@

%	\begin{lemma}
%		\label{lemma2}
%		Let $L,L'$ be consecutive layers of a compensation free DNN, and $n \in L'$. 
%		Then:
%		$$ S(n) \max(S(n) n)=\sum_{m \in L}weigth(m n) S(m) \max(S(m) \hat{m})+bias_n \text{ and }$$
%		$$S(n) \max(S(n)\hat{n}_s)=\ReLU(\sum_{m \in L}weigth(m n) S(n)\max(S(n)\hat{m}_s)+bias_n)$$
%		
%		Similarly for minimal value.
%		
%		%	for minimal value,	
%		%	$ \min(n)=\sum_{m \in L}W_{m n)\min(\)+bias_n $ and
%			%	$ \min(\hat{n}_s)=ReLU(\sum_{m \in L}weigth(m n)\min(\hat{m)s}+bias_n)$
%		\end{lemma}
%		
%		\begin{proof}
%			We choose $\boldsymbol{x}^*$ maximizing each $a_s \in \{a,-a\}$ in the input layer $L=L_0$,
%			that is setting the value for node $a$ be $\max(a)$ for $S(a)=1$ and $\min(a)$ for $S(a)=-1$.
%			At configuration $\boldsymbol{x}^*$, every $a_s(\boldsymbol{x}^*))=\max_{\boldsymbol{x}} {a_s(\boldsymbol{x}))}=\max(a_s)$ is maximized.  
%			
%			Consider any $b$ in the first hidden layer $L_1$.
%			Assume first that $S(b)=+1$.
%			We have $\Val(b_s)= \Val(b) = \sum_{a \in L_0} weigth(ab) \Val(a) + bias_b$.
%			If every $weigth(ab) \Val(a)$ is maximized in the same time, 
%			then $\Val(b_s)= \Val(b)$ is also maximized. 
%			
%			We claim that this is the case at 
%			configuration $\boldsymbol{x}^*$.
%			Indeed, if $weigth(ab)=0$, any $\Val(a)$ can be chosen to maximize 
%			$weigth(ab)\Val(a)$. If $weigth(ab)>0$ then $S(a) = +1$ by Lemma \ref{lemma1}, since
%			$S(b)=+1$. We have $\max(a_s) = \max(a)$, maximizing $weigth(ab)\Val(a)$.
%			Finally, if $weigth(a b)<0$ then $S(a_s) = -1$, and we have 
%			$\max(a_s) = min(a)$, maximizing $weigth(ab)\Val(a)$.
%			
%			Hence $b$ reaches is maximum in configuration $\boldsymbol{x}^*$, and the value satisfies: 
%			$$\max(b)=\sum_{m \in L}weigth(a b) \max(a_s)+bias_b$$
%			
%			The case $S(b)=-1$ is symmetric:
%			$\max(b_s)= -\min(b)$ is reached when minimizing $b$, which is also 
%			satisfied at $\boldsymbol{x}^*$.
%			In both case, $\Val(b_s)$ is maximized at $\boldsymbol{x}^*$. Notice that $\boldsymbol{x}^*$ does not depend upon $b$, so choosing $\boldsymbol{x}^*$ uniformly maximize all $\Val(b_s)$.
%			
%			This implies that $\ReLU(b_s)$ is maximized at $\boldsymbol{x}^*$, and its value is 
%			$\ReLU(\sum_{m \in L}weigth(a )\max(a_s)+bias_b)$, again uniformly reached over all $b$ at configuration $\boldsymbol{x}^*$.
%			
%			We proceed by induction over every layer of the DNN till the output layer, proving that 
%			$\max(z_s)=\max(z)$ is reached at configuration $\boldsymbol{x}^*$.
%			
%			The case for $\min$ is similar, with another input vector $\boldsymbol{x}^\sharp$ instead of $\boldsymbol{x}^*$.
%			\hfill $\square$
%		\end{proof}

@@

		\begin{corollary}
			\label{cor1}
			$$\max(c)=\sum_{b \in L, weigth(bc)>0}weigth(bc) \max(\hat{b}) + \sum_{b \in L, weigth(bc)<0}weigth(bc) \min(\hat{b}) + \boldsymbol{bias}_c$$
			$$\min(c)=\sum_{b \in L, weigth(bc)>0}weigth(bc) \min(\hat{b}) + \sum_{b \in L, weigth(bc)<0}weigth(bc) \max(\hat{b}) + \boldsymbol{bias}_c$$
		\end{corollary}

@@

			The Box absraction computes its upper bound using:
			$$\bar{f}(n)= \sum_{weigth(mn)>0} weigth(mn) \bar{f}(\hat{m}) + \sum_{weigth(mn)<0} weigth(mn) \underline{f}(\hat{m}) + bias_n$$

@@

				%	 \item $weigth(b,z)=0$, or
				%	 \item For every input node $j\in J$, we have $weigth(a_j,b)=0$.

@@

			%	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $weigth(a_j,b)=0$ implies weight$(\pi)=0$.

@@

			%	Because 2) does not hold, there is a $j \in J$ with $weigth(a_j,b) \neq 0$, say $>0$.
			%	Because 1) does not hold, $weigth(b,z) \neq 0$, say $>0$.

@@

			%	$$b= B^0 +\sum_{a_i\in I} weigth(a_i, b) a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.

@@

			%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}weigth(b_ha_i)+B_h$ ($B_h$ is the bias). 

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_{open}} weigth(b,z)\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).

@@

			%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $weigth(b,z)>0$, and the lower bound
			%of its (LP) approximation if $weigth(b,z)<0$. 

@@

			%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(weigth(zb))=1$, then 

@@

			%and if $S(b)=\mathrm{sign}(weigth(zb))=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.

@@

			%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_{open}} weigth(b,z)\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
			%	\sum_{b\in B_{pure}} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).

@@

			%$weigth(b,z) = 0$ and $b \in B^2$ iff $weigth(b,z) \neq 0$.

@@

			%$$\sum_{b\in B_{pure}} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$

@@

			%For $b \in B^2$, we have $weigth(a_j,b)=0$ for all $j \in J$

@@

			%$$\sum_{b\in B^2} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
			%\sum_{b\in B^2} weigth(b,z) \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
			%=\sum_{b\in B^2} weigth(b,z) \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))

@@

				%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}weigth(zb)\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))

@@

				\begin{lemma} \label{lem:open_node_2}
					A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
					\begin{enumerate}
					  	\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $weigth(b,z)=0$ to denote this case, or
						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $weigth(a_j,b)=0$ to denote this case.
					\end{enumerate}

@@

				\begin{proof}
					First, we show that if one of case 1, 2 happens, then $b$ will not be on a weak compensating pair. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $weigth(a_j,b)=0$ implies weight$(\pi)=0$.

					Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
					Because 2) does not hold, there is a $j \in J$ with $weigth(a_j,b) \neq 0$, say $>0$.
					Because 1) does not hold, $weigth(b,z) \neq 0$, say $>0$.
					Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
					from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
					Then $((a_j,b,z), \pi')$ is also a weak compensating pair. \qed
				\end{proof}

				\begin{lemma}\label{lem:subnetwork}
					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $weigth(bc)=0$. We call this sub-network $D_I$. In $D_I$, there is no compensating pair.
				\end{lemma}

@@

					1. if $b\in J$, by definition, $weigth(bc)=0$.

					2. if $b\in B_{open}$, then $weigth(bc)=0$; otherwise there exists $<a_j,b,c>$ a path from $a_j\in J$ to $c$ with a nonzero value, a contradiction.

					3. if $b\in B_{zero}$, then $weigth(bc)=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction. \qed
				\end{proof}

@@

				\begin{lemma}
					If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $weigth(bc)\neq 0$, then $weigth(bc)S(c)=S(b)$.
				\end{lemma}

@@

				\begin{proof}
					This is because if there exists nodes $b,c$ such that $weigth(bc)\neq 0$ and $c$ is in above set but $b$ is not, then $b$ has a path with nonzero weight from a node $a_i$ not in $J$ but this means so does $c$, a contradiction. Therefore any $b$ such that $weigth(bc)\neq 0$ is also in above set. \qed
				\end{proof}

@@

				%\begin{lemma}\label{lem:pure_node}
				%	For a node $c\in B_{pure}$, $\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}$ (and $\LB$ the same) only depends on $\boldsymbol{x}^0_I$.
				%\end{lemma}
				%
				%\begin{proof}
				%	We prove this lemma by induction. For the first hidden layer, this is trivial.
				%	
				%	Suppose for layer up to $l_i$, this lemma is true, we show it for layer $l_{i+1}$. For a node $c$ in layer $l^{i+1}$, we have that: \begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{open}\cap l_i} weigth(b,c)\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))\\
					%		 +\sum_{b\in B_{zero}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} Here, $\B$ means one of $\UB$ or $\LB$ depending on the weight/coefficient.
				%	
				%	
				%	But since $c\in B_{pure}$, for any $b\in B_{open}$, we must have $weigth(b,c)=0$. And similarly, for any $b\in B_{zero}$, $weigth(bc)=0$. Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) \leq B_c + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
					%	\end{align*} By induction, for any $b\in B_{pure}\cap l^i$, it only depends on $\boldsymbol{x}^0_I$.  Therefore, we will have:
				%	
				%	\begin{align*}
					%		\UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c) = B_c + \sum_{b\in B_{pure}\cap l_{i}} weigth(b,c) \mathrm{AppB}(B_{\boldsymbol{x}^0_I}(b)).
					%	\end{align*} So, $UB_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(c)$ only depends on $\boldsymbol{x}_I^0$.
				%\end{proof}

@@

					If $S(c)$ is defined, then consider all $b$ such that $weigth(bc)\neq 0$. First, $b$ cannot in $B_{zero}$; so by induction hypothesis, the value of $b$ is fixed under $\boldsymbol{x}^*_I,\boldsymbol{x}^0_J$ in MILP model.
